{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-14 Meetings/GPMNov2017/gpm_november2017_topic21.tex
Update to GPM
small correction from Volker

\begin{frame}{2017 Top Objectives 
    12.12.2016}
  \Fontvi
\vspace{-1cm}
Deliverables listed during the call for manning of last December 
\begin{enumerate}
\item \only<2>{\color{ta3chameleon}} Cross-machine L-Mode
  shoulder dependence on current both at constant B$_t$ and at
  constant $q_{95}$. Rationale: disentangle the effect of current and
  parallel connection length
\item \only<2>{\color{taorange}}Establish robust scenario for density
  shoulder profile in H-Mode and establish dependence on
  fuelling/neutral profiles/divertor condition
\item \only<2>{\color{ta3chameleon}}Use the new HHF probe on AUG to study
  filamentary transport under high-power H-Mode conditions \only<2>{\color{consorziored}}and under
  different plasma configurations (SN, DN)
\item \only<2>{\color{taorange}}Study the role of ELM regimes,  neutral
  compression and particle density in filamentary transport and
  related shoulder formation
\item \only<2>{\color{taorange}} Identify the contribution of
  collisionality and seeding on filamentary transport and related
  shoulder formation
\item \only<2>{\color{consorziored}}Determine the effect of filaments and
  shoulder formation on target heat loads in different H-mode plasmas
\end{enumerate}
\onslide<2>{
  So far H-Mode operation has been limited to AUG since no operational
  scenario in high-density NBH heated plasma on TCV has been established
}
\end{frame}

>>>>

\begin{frame}{Motivation and deliverables}
  \Fontvi
  \vspace{-1cm}
  \begin{itemize}
    \item \alert{Relation between downstream divertor conditions and
        up-stream SOL profiles is not well understood. Influence of
        SOL blob structures on shoulder formation and divertor
        conditions is element towards predictive capabilities. }
  \end{itemize}
  \onslide<2->{Deliverables listed during the call for manning of last December
\begin{enumerate}
\item \only<3>{\color{ta3chameleon}} Cross-machine L-Mode
  shoulder dependence on current both at constant B$_t$ and at
  constant $q_{95}$. Rationale: disentangle the effect of current and
  parallel connection length
\item \only<3>{\color{taorange}}Establish robust scenario for density
  shoulder profile in H-Mode and establish dependence on
  fuelling/neutral profiles/divertor condition
\item \only<3>{\color{ta3chameleon}}Use the new HHF probe on AUG to study
  filamentary transport under high-power H-Mode conditions \only<3>{\color{consorziored}}and under
  different plasma configurations (SN, DN)
\item \only<3>{\color{taorange}}Study the role of ELM regimes,  neutral
  compression and particle density in filamentary transport and
  related shoulder formation
\item \only<3>{\color{taorange}} Identify the contribution of
  collisionality and seeding on filamentary transport and related
  shoulder formation
\item \only<3>{\color{consorziored}}Determine the effect of filaments and
  shoulder formation on target heat loads in different H-mode plasmas
\end{enumerate}}
\onslide<3>{
  So far H-Mode operation has been limited to AUG since no operational
  scenario in high-density NBH heated plasma on TCV has been established
}
\end{frame}
